Prag Bat Round 2

### 2020-11-02 analysis/data_round3.Rmd
add new stimuli for rmts and change timing

```{r}
files <- dir("~/Work/Local/PragBat/raw_data2/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/Local/PragBat/raw_data2/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,34,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date,
                                               trial = as.character(trial))
  raw_data <- bind_rows(raw_data, id)
}

@@

log <- read_xlsx("../../../../Cloud/PragBat/vpl_pragBat2.xlsx", sheet = 1)%>%
  mutate(age = as.numeric(difftime(as.Date(as.character(test_day_1),format="%Y%m%d"), as.Date(as.character(birthday),format="%Y%m%d"), units = "days"))/365.25,
         age_num_month = lubridate::time_length(difftime(as.Date(as.character(test_day_1),format="%Y%m%d"), as.Date(as.character(birthday),format="%Y%m%d")), "month"),
          age_month = round(age_num_month)/12,
         id = paste("VP",ID, sep = ""))%>%
  select(id, age, age_month, status)

@@

# Discourse continuity by category

```{r}

con_data <- task_data%>%
  filter(task == "discourse_continuity")%>%
  filter(!is.na(correct))

pc1 <- con_data%>%
  group_by(target1,subage, id) %>%
  summarise(correct = mean(correct))

pc2 <- pc1 %>%
  group_by(target1,subage) %>%
  tidyboot_mean(column = correct)

ggplot()+
  geom_hline(yintercept = 1/3, lty=2)+
  geom_jitter( data = pc1, aes(x = subage, y = correct, col = target1), position = position_jitterdodge(jitter.width = .1,jitter.height = .025, dodge.width = .75 ), alpha = .3)+
  geom_pointrange(data = pc2, aes(x = subage, y = mean, ymin = ci_lower, ymax = ci_upper, col = target1), position = position_dodge(width = .75), pch = 4)+
  #facet_grid(~experiment)+
  labs(x="Age",y="Proportion correct")+
  theme_few()+
  scale_color_colorblind(name = "Category")
```

# Data file Spin-off

```{r}
item_info <- data_frame(
  task = c(rep("mutual_exclusivity",10),rep("simple_inf",10),rep("ad_hoc_implicature",10)),
  trial = c(rep(1:10,3)), 
  item = c(rep(c("carrot","garlic","eggplant","duck","horseshoe"),2),rep(c("bear","robot","rocket","truck","dino"),2), rep(c("box","chair","table","plate","house"),2))
)

retest_ids <- data %>%
  filter(test_day == 2)%>%
  group_by(id)%>%
  summarise(n())%>%
  pull(id)

data %>%
  filter(task == "mutual_exclusivity" |
         task == "simple_inf" |
         task == "ad_hoc_implicature",
         id %in% retest_ids)%>%
  select(-agent, -z_age, -z_trial)%>%
  left_join(item_info)%>%
  select(id, test_day, subage, age, age_month, task, trial, item, correct )%>%
  mutate(c_age_month = age_month - min(age_month),
         c_age = age - min(age))%>%
  write_csv("../../../Spin-off/spin-off/data/data.csv")
```

>>>>

```{r}
files <- dir("~/Work/Local/PragBat/raw_data3/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/Local/PragBat/raw_data3/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,-22,str_length(jf)-14)
  id <- as_data_frame(jd) %>% mutate(test_date = date,
                                              trial = as.character(trial))
  raw_data <- bind_rows(raw_data, id)
}

@@

log <- read_xlsx("../../../../Cloud/PragBat/vpl_pragBat3.xlsx", sheet = 1)%>%
  mutate(age = as.numeric(difftime(as.Date(as.character(test_day_1),format="%Y%m%d"), as.Date(as.character(birthday),format="%Y%m%d"), units = "days"))/365.25,
         age_num_month = lubridate::time_length(difftime(as.Date(as.character(test_day_1),format="%Y%m%d"), as.Date(as.character(birthday),format="%Y%m%d")), "month"),
          age_month = round(age_num_month)/12,
         id = paste("VP",ID, sep = ""))%>%
  select(id, age, age_month, status)

@@
